---
title: "Competitive Pokemon Analysis"
author: "Ricky Warner"
date: "12/1/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Background 

As many of my friends and family can atestify, I am a very big fan of pokemon. I have been playing since I was very little when I got my first pokemon game: Pokemon Colosseum. Despite my many years of playing pokemon, I have a confession to make: I am not a very good competitive player. My teams have always been mainly favorites I've found while travelling in the games. While it's usually enough to get through the game, it's not enough to face people head on competitively. After awhile I had the realization. I have a background in data science, why not use that to help me design a perfect team? And so, after a bit of work, the following analysis was born. 

## About the Data 
The dataset was compiled by me using the PokeApi website (url: https://pokeapi.co/). If you are interested in viewing the code that I used to compile the dataset, please go [here](insert link when you upload to github) 


```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
